Is structure based drug design ready for selectivity optimization?

### 2018-11-28 manuscript.tex
adding author contributions

\section{Author Contributions}
\textbf{to be filled out soon} \\
 designed the research; 
 identified experimental datasets; 
 performed the simulations; 
 analyzed the data; 
 wrote the paper.

>>>>

\section{Author Contributions}
Conceptualization: SKA, LW, RA, JDC \\
Methodology: SKA, LW, JDC\\
Investigation: SKA, SP\\
Writing -- Original Draft: SKA\\
Writing -- Review \& Editing: SKA, JDC \\
Funding Acquisition: RA, JDC\\
Resources: LW, JDC\\
Supervision: LW, JDC
